Formation of porous crystals via viscoelastic phase separation

### 2016-12-20 nature/Supplementary.tex

\section*{Supplementary Movie 2}
Same as the end of Supplementary Movie 1, but with computer rendered trajectories obtained from the tracking of the colloidal particles. Particles are coloured according to the following code: crystal (red), surface (blue), gas (green) and liquid (white). For display purposes, crystalline particles and gas particles are respectively 400\% and 50\% bigger than other particles (liquid or surface).

>>>>

\section*{Supplementary Movie 2}
This movie shows the 3D structural evolution in the gelation process of $\phi\approx 0.30$ and $c_p=0.40$ mg/g in a capillary cell. 
We show computer rendered trajectories obtained from the tracking of the colloidal particles. Particles are coloured according to the following code: crystal (red), surface (blue), gas (green) and liquid (white). For display purposes, crystalline particles and gas particles are respectively 400\% and 50\% bigger than other particles (liquid or surface).
